AusTraits -- a curated plant trait database for the Australian flora

### 2020-11-10 ms.Rmd
Update data to 2.1.0

```{r authors}
authors_lead <- read_csv("data/lead_authors.csv", col_types = cols(.default = "c"))

# check list of acknowledgments and assistants

data_contributors <- 
  austraits$contributors %>% 
    mutate(name = gsub("Richard Duncan", "Richard P. Duncan", name, fixed=TRUE)) %>%
    mutate(
      acknowledge = ifelse(
          # old studies or excluded
          dataset_id %in% c("Lawes_2012", "Westman_1977", "Hall_1981", "Hocking_1982", "Hocking_1986", "Toelken_1996", "Brock_1993", "Forster_1992", "Forster_1995", "Goble_1981") |
           role %in% c("assistant") |
           # deceased
           name %in% c("Peter Clarke", "Barbara Rice", "Peter Myerscough", "Lyn Craven", "Harold Trevor Clifford", "William Cooper") |
            # no response or can't locate
           name %in% c("Emma Laxton", "Huw Morgan", "Wendy Cooper", "Muhammad Islam", "Michael Lawes"),
            TRUE, FALSE),
      year = dataset_id %>% str_split_fixed("_", 4) %>% .[,2]) %>% 
    arrange(year) %>%
    # take most recent address for each author
    group_by(name) %>% 
    summarise(institution = last(institution),
              dataset_ids = paste(dataset_id, collapse = ", "),
              acknowledge = all(acknowledge)) %>% 
    ungroup() %>% 
    distinct() %>% 
    mutate(surname = str_split(name, " ") %>% map_chr(last)) %>% 
    rename(affiliation = institution) %>%
    arrange(surname) %>% 
    select(-surname)

authors <- bind_rows(authors_lead, 
                     data_contributors %>% filter(! (name %in% authors_lead$name), !acknowledge)
                    )

acknowledge <- data_contributors %>% filter(! (name %in% authors$name), acknowledge)

authors %>% select(dataset_ids, everything()) %>% mutate_all(~ replace_na(.x, "")) %>% write_csv("data/author_list.csv")

# Update author info from google sheets

@@

![Coverage of georeferenced trait records across Australian climatic and geographic space for traits in different categories. (a.) AusTraits’ sites (orange) within Australia’s precipitation-temperature space (dark-grey) superimposed upon Whittaker’s major biomes diagram. Climate data were extracted from Worldclim \citep{Fick-2017}.(B.) Locations of geo-referenced records for different plant tissues. ](figures/austraits_fig_biome_map.pdf)

>>>>

```{r authors}
data_contributors <- read_csv("data/author_list.csv")
authors <- data_contributors %>% filter(!acknowledge)
acknowledge <- data_contributors %>% filter(acknowledge)

@@

![Coverage of georeferenced trait records across Australian climatic and geographic space for traits in different categories. (a.) AusTraits’ sites (orange) within Australia’s precipitation-temperature space (dark-grey) superimposed upon Whittaker’s major biomes diagram. Climate data were extracted from Worldclim \citep{Fick-2017}.(B.) Locations of geo-referenced records for different plant tissues. ](figures/austraits_fig_biome_map.png)
